---
title: "eNFI Lesson 2.2: Simple sampling for carbon - Analysis"
# output: word_document ## Uncomment for docx output and comment other outputs + runtime
output:
  learnr::tutorial:
    progressive: true
    allow_skip: false
    # css: 
    #   - css/custom.css
    #   - css/fonts.css
    #   - css/style.css
    #   - css/banner-style.css
    #   - css/toc-style.css
    includes:
      in_header: 
      - html/header.html
      - !expr system.file("tuto-helpers/css/custom.html", package = "eNFI")
      - !expr system.file("tuto-helpers/css/fonts.html", package = "eNFI")
      - !expr system.file("tuto-helpers/css/style.html", package = "eNFI")
      - !expr system.file("tuto-helpers/css/banner-style.html", package = "eNFI")
      - !expr system.file("tuto-helpers/css/toc-style.html", package = "eNFI")
runtime: shiny_prerendered
description: >
  Analyze forest inventory data from a systematic sampling design. 
---

```{r setup, include=FALSE}

library(learnr)
knitr::opts_chunk$set(echo = FALSE)

library(gradethis)
gradethis::gradethis_setup()


#load("data/solutions-lesson1.Rda")

## Setup
library(tidyverse)

library(sysfonts)
library(showtext)

library(eNFI)

sysfonts::font_add("Lora", system.file("fonts/lora-v23-latin-italic.ttf", package = "eNFI", mustWork = T))
sysfonts::font_add("Shadow", system.file("fonts/shadows-into-light-v14-latin-regular.ttf", package = "eNFI", mustWork = T))
showtext::showtext_auto()

## Load data
#load(system.file("extdata/louland_param.Rda", package = "eNFI"))

louland_param <- tibble(
      lc_id   = 0:6, 
      lc      = c("WA", "NF", "WL", "DD", "MD", "EV", "MG"),
      lc_name = c("Water", "Non-forest", "Woodland", "Deciduous", "Mixed-deciduous", "Evergreen", "Mangrove"),
      w       = c(0, 0.37, 0.21, 0.08, 0.23, 0.11,  0),
      hex     = c("#73c2fb", "#edf5e1", "#ffcb9a", "#5cdb95", "#379683", "#00743f", "#012172")
    ) %>%
  mutate(lc_name = fct_reorder(lc_name, lc_id))

load(system.file("extdata/louland_lc.Rda", package = "eNFI"))
load(system.file("extdata/louland_admin.Rda", package = "eNFI"))
load(system.file("extdata/sf_exfi.Rda", package = "eNFI"))

load(system.file("extdata/solutions-lesson1.Rda", package = "eNFI"))


```


## Topic 1

### Exercise 


Test: this is part of the data corrections tables:

```{r, echo=T}

print(summary(exfi_agb))

```



*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
